---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dev = "svg"
)
```

# rgeoboundaries

<!-- badges: start -->

[![Project Status: Active - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![GitLab CI Build Status](https://gitlab.com/dickoa/rgeoboundaries/badges/master/pipeline.svg)](https://gitlab.com/dickoa/rgeoboundaries/pipelines)
[![CRAN status](https://www.r-pkg.org/badges/version/rgeoboundaries)](https://cran.r-project.org/package=rgeoboundaries)
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)

`rgeoboundaries` is an R client for the [GeoBoundaries API](https://www.geoboundaries.org/)

<!-- badges: end -->

## Installation

You can install the development  version of rgeoboundaries using the `remotes` package:

``` {r, eval = FALSE}
# install.packages("remotes")
remotes::install_gitlab("dickoa/rgeoboundaries")
```

## Access administrative boundaries using rgeoboundaries

This is a basic example which shows you how get Senegal administrative level 3 boundaries and plot it

```{r plot}
library(rgeoboundaries)
library(sf)
mli_sen <- gb_adm1(c("mali", "senegal"))
plot(st_geometry(mli_sen))
```

```{r, metadata}
knitr::kable(gb_metadata(c("mali", "senegal"), "adm1"))
```

## How to to cite

If you are using this package in your analysis, please cite the original `geoBoundaries` work:

> Runfola, D., Seitz, L., Hobbs, L., Panginaban, J., Oberman, R. et al. geoBoundaries Global Administrative Database. http://www.geoboundaries.org.